\chapter{\label{ch:5}Integration of Single Cell Atlas with Slide-seq Profiling in Breast Cancer}

\section{Introduction}
The intention for my final results chapter was to integrate dissociated single cell sequencing data with spatial transcriptomic data in breast cancer in order to provide insight on spatially distinct transcriptional profiles which could guide future therapeutic development.


\section{Results}

\subsection{Integration of Paired Single Cell Profiling with Slide-seq Profiling in Breast Cancer}
The production of Slide-seq data has been delayed during the pandemic. I have made exhaustive efforts to make progress on this work within the time-frame of my DPhil. The data has not been available in time for exploration as part of my thesis. There is no published Slide-seq cancer data to provide guidance on potential insight or intended results. It has therefore not been possible to complete this section owing to the exceptional delays and disruption caused by the pandemic. 

\subsection{Identification of spatially Distinct Transcriptional Responses Conserved amongst Different Patient Samples}
Data required for the completion of this section is pending owing to the exceptional delays and disruption caused by the pandemic. 

\subsection{Integration of Slide-seq Profiling with an Unpaired Single Cell Atlas}
Data required for the completion of this section is pending owing to the exceptional delays and disruption caused by the pandemic. 

\subsection{Comparison of Different Single Cell Atlases in Breast Cancer and Integration with Slide-seq Profiling}
Data required for the completion of this section is pending owing to the exceptional delays and disruption caused by the pandemic. 

\section{Discussion}
Once available, the results will warrant analysis to provide insight on spatially profiled gene expression in clinical breast cancer.




